---
title: "Assignment 5"
author: "Ranadheer Gonuguntla"
date: "2023-11-30"
output:
  pdf_document: default
  html_document: default
---

Loading required libraries

```{r}
library(factoextra)
library(dendextend)
library(cluster)
library(tidyverse)
library(knitr)

```

Importing the data
```{r}

Data_cereals = read.csv("C:\\Users\\sidda\\Downloads\\Cereals (2).csv")
numerical_data = data.frame(Data_cereals[,4:16])

```
Removing all the missing values present in the data

```{r}

Data_nomissingValues = na.omit(numerical_data)

```

Normalizing the data
```{r}
Normalised_data = scale(Data_nomissingValues)
```

Measuring the distance using the euclidian distance 
```{r}

Data_distance = dist(Normalised_data, method = "euclidian")
```
Performing hierarchial clustering using complete linkage

```{r}

hierarchial_clustering = hclust(Data_distance,method = "complete")
plot(hierarchial_clustering)
```

Rounding off the decimals
```{r}
round(hierarchial_clustering$height, 3)
```




Performing clustering using AGNES
```{r}
library(dendextend)

HC_single = agnes(Normalised_data, method = "single")
HC_complete = agnes(Normalised_data, method = "complete")
HC_average = agnes(Normalised_data, method = "average")
HC_ward = agnes(Normalised_data, method = "ward")
```

Lets Compare the agglomerative coefficients of single , complete, average, ward

```{r}

print(HC_single$ac)
print(HC_complete$ac)
print(HC_average$ac)
print(HC_ward$ac)

```

from the above values, ward method is the best as it has the agglomerative coefficient value of 0.904.\
Lets determine the optimal clusters\


```{r}

#using the ward method for hierarchial clustering
HC_1 <- hclust(Data_distance, method = "ward.D2" )
plot(HC_1,cex=0.6)
rect.hclust(HC_ward,k=5, border=2:10)
```

from the above result of ward method graphs, it can be seen that the k value is considered as 5.So we would choose 5 Clusters.\
Lets plot agnes using the ward method

```{r}
subgroup = cutree(HC_1,k=5)
table(subgroup)
cereals_groups <- as.data.frame(cbind(Normalised_data,subgroup))
```

Lets visualise the results on scatterplot
```{r}
fviz_cluster(list(data = Normalised_data, cluster = subgroup))
```

Lets find the best breakfast cereal cluster with high protein, fibre and low in sugar and sodium.\

choosing the healthy cereal cluster
```{r}
New_cereals = numerical_data
New_cereals_omit = na.omit(New_cereals)
Cluster = cbind(New_cereals_omit, subgroup)
Cluster[Cluster$subgroup==1,]
```

```{r}
Cluster[Cluster$subgroup==2,]
```


```{r}
Cluster[Cluster$subgroup==3,]
```


```{r}
Cluster[Cluster$subgroup==4,]
```


```{r}
Cluster[Cluster$subgroup==5,]
```

in order to determine the healthy cluster cereals, lets calculate the mean rating 
```{r}
mean(Cluster[Cluster$subgroup==1,"rating"])
mean(Cluster[Cluster$subgroup==2,"rating"])
mean(Cluster[Cluster$subgroup==3,"rating"])
mean(Cluster[Cluster$subgroup==4,"rating"])
mean(Cluster[Cluster$subgroup==5,"rating"])

```

It is clear from the figures above that subgroup 1 has the highest mean rating of 73.84446. Therefore, subgroup 1 should be selected as the cluster for the healthy diet.






```{r}


```

```{r}


```
